% This is compiled and printed on the back of the board!

\documentclass{article}
\pagenumbering{gobble}

\usepackage[papersize={10in,10in},margin=0.5in]{geometry}
\usepackage{fontspec}
\usepackage{multicol}

\setmainfont{GFS Didot}
\newfontfamily\Racing{Faster One}

\usepackage{lipsum}

\begin{document}
\begin{multicols}{3}

{\noindent\fontsize{24}{24}\Racing How to play\par}

\vskip0.3em
\hrule
\vskip1em
{\noindent\fontsize{18}{18}\Racing Setup\par}

    To begin the game separate out the upgrade cards from the rest of the cards. You
    should be left with the starter cards (grey border), the special cards
    (lots of text, no image), and the stretch cards (have a distance at the
    bottom).

    Separate the starter cards into 4 equal decks (with the exact same cards in
    them). For reference, each player should begin with the cards listed on the
    list card in their deck.

    Setup the rest of the game by giving each player a starting deck, a red die,
    a blue die, and a token. Their token should be placed before the starting
    line on the map.

{\noindent\fontsize{18}{18}\Racing Objective\par}

    This is a race. Just like the real iditarod your goal is to be the first to
    travel 1600km (160 myriameters). Each square on the board is a single
    myriameter, so there are 160 of them.

{\noindent\fontsize{18}{18}\Racing Costs\par}

    The core mechanic of this game is the way in which costs on cards are
    played.

    When a card is played the three costs are resolved in order.

    First, the player must discard the "energy" cost (blue number) of the card
    from their hand.

    Second, the player must discard the "health" cost (red number) of the card
    from the top of their deck. If the player fails to pay either cost, the card
    does nothing.

    Finally the player must resolve the "risk" of the card.

{\noindent\fontsize{16}{16}\Racing Risk\par}

    Whatever the risk (black number) of a card is, that many cards must be
    played on the subsequent turns successfully. Only once all such cards are
    played does the effect of the original card take place.

    If another risk occurs as payment for a risk they do stack, but once the
    risk of the second card is paid its effect happens even if the original risk
    card's effect has not.

    If at any point you cannot afford the cards being played as risk, the risk
    card fizzles and does nothing.

{\noindent\fontsize{18}{18}\Racing New Days\par}

    On any turn a player may choose to take a new day instead of playing a card.
    In this case any current risks are abandoned and the player shuffles their
    discard pile and hand into their deck. They then draw a new starting hand.

    The starting hand is, by default, 6 cards. This number is frequently
    modified however.

{\noindent\fontsize{18}{18}\Racing Destruction\par}

    There is an important distinction between discarding and destroying a card.
    When a card is discarded it is merely added to its player's discard pile and
    will return to their deck when they take a new day. A card which is
    destroyed is removed from play and will not be used in the current game ever
    again.

{\noindent\fontsize{18}{18}\Racing Stretch Effects\par}

    Each stretch has a unique effect when you enter it. Like other cards,
    stretches may have red and blue numbers on them. These set your starvation
    and hypothermia respectively.

    Starvation increases the health (red) cost of every card by 1 for each
    starvation you have. This does not apply to cards with no health cost to
    begin with. Keep track of starvation on your sled card using the red die.

    Hypothermia increases the energy (blue) cost of every card by 1 for each
    hypothermia you have. This does not apply to cards with no energy cost to
    begin with. Keep track of hypothermia on your sled card using the blue die.

    If either your starvation or hypothermia reaches a level of 6 you have died.
    Move back 30 myriameters and set your starvation and hypothermia to that of
    your current track. If you move beyond the town you will have 0 starvation
    and hypothermia.

    All stretch effects take precedent over other effects. This means that they
    occur first.

{\noindent\fontsize{18}{18}\Racing Special Effects\par}

    Recover allows you to move the specified number of cards from your discard
    pile into either your hand or your deck. The choice is yours.

    When you pass a player on the board you take 1 damage and they are moved
    back 1 square. This process occurs iteratively, so there can never be two
    players on the same space of the board (except before the starting line).
    The direction of movement does not matter, if you become further ahead of
    someone you take a damage and they move back one, even if they were moving
    backwards.

{\noindent\fontsize{18}{18}\Racing Card Types\par}

    The following is a summary of how each card type works:

    \begin{itemize}
        \item Dog cards are brown. When you play a dog it stays in front of you
            and provides a passive bonus. You may only have 6 dogs at a time,
            but may kill a dog whenever you wish. A killed dog is destroyed (not
            discarded).

        \item Attachment cards are blue. You must play an attachment on a dog
            and dogs may only hold one attachment each. You may not remove an
            attachment once played. Like dogs, attachments provide passive
            bonuses. When the dog an attachment is on is killed, that attachment
            is discarded.

        \item Food cards are yellow. As soon as you play a food card your
            starvation is reduced by 1. This happens before payment and whether
            or not payment succeeds.

        \item Personal cards are purple. As soon as you play a personal card
            your hypothermia is reduced by 1. This happens before payment and
            whether or not payment succeeds. Personal cards typically have the
            text "Destroy up to X of Y" on them. This means that you look at the
            top Y cards of your deck, choose up to X of them to destroy, then
            choose which of the remaining cards to shuffle back into your deck
            and which to draw into your hand. Using a personal card is referred
            to as "healing".

        \item Sled cards are green. They typically have the text "Take X of Y"
            on them. This means that you look at the top Y cards of the upgrade
            deck, choose X of them to place in your discard pile, and destroy
            the rest. As they are immediately discarded all other players may
            see what they are. Additionally you may not use them until the next
            day (unless you recover them).

        \item Utility cards are white. They tend to be interactive. They have no
            effect whatsoever when you are immune. This means that they do
            nothing if you play them, and do not effect you if someone else
            plays them. Remove the utility cards from the game when playing
            solitaire.

        \item Movement cards are blue. When you play a movement card add your
            current speed to its effect.
    \end{itemize}

\end{multicols}
\end{document}
